On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-04 main.tex
Update main.tex
Some corrections

%% %
%% \subsubsection{Critical points of polynomial mappings}
%% %
%% Let $\phi : V \rightarrow \C^m$ be a polynomial mapping. A \textit{critical point} of $\phi$ is a regular point of $V$ with $d_x \phi(T_xV) \not = \C^m,$ where $d_x \phi$ is the differential of $\phi$ at $x.$ A \textit{critical} value of $\phi$ is the image of a critical point by $\phi$.
%% %
%% \subsection{The zariski-tangent space}
%% %
%% Denote by $\grad_{\xb}(f)$ the evaluation of the gradient vector of $f$ in $\C[X_1,\hdots,X_n]$ at $\xb$ in $\C$.
%% The \textit{Zariski-tangent space} to $V$ at $\xb \in V$ is the vector space $T_{\xb}V$ defined by the equations $\grad_{\xb}(f) \cdot \textit{\textbf{v}}=0$ for all polynomials $f$ that vanish on $V$. For a polynomial system $\textit{\textbf{f}}=(f_1,\hdots,f_N)$ in $\C[X_1,\hdots,X_n]$, denote by $\jac(\textit{\textbf{f}})$ the Jacobian matrix.
%% The following is a direct consequence of \cite[Corollary 16.20]{ECA}.
%% %
%% \begin{proposition}
%% If $V \subset \C^n$ is a $d$-equidimensional algebraic set with ideal $I(V)=\langle f_1,\hdots,f_N \rangle$, then at any point $\textbf{x}$ of $\reg(V),$ $\jac_\textbf{x}(\textbf{f})$ has full rank $n - \dim(V)$ and the kernel of $\jac_\textbf{x}(\textbf{f})$ is equal to $T_\textbf{x}V.$ 
%% \end{proposition}
%% %
%% \subsection{Polar varieties}
%% %
%% %
%% \subsection{Changes of variables}
%
Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \xb \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
$V^A$ the set $\{x^A~|~\xb \in V\}, f^A$ the polynomial $f(A \xb)$ and $\xb^A$ denotes $A^{-1}\xb$. Notice $f^A(\xb^A) = f(A A^{-1}\xb)=f(\xb).$
%
%
%
%
%
%
%
%
\section{Genericity properties}
%
Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $D$.  
We say that $f$ satisfies $\textbf{H}$ if 
%
\begin{enumerate}
    \item $f$ is squarefree;
    \item $V(f)$ is smooth.
\end{enumerate}
%
An equidimensional algebraic set $X$ of dimension $d$ is in \textit{Noether position} for $\pi_d$ when the extension 
\[
\C[X_1,\hdots,X_d] \rightarrow \C[X_1,\hdots,X_n]/I(V)
\] 
is injective and integral.  Then, for any $\xb \in \C^d,$ the fiber 
$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (x_1,\hdots,x_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
%
\begin{enumerate}
\item $\I(\pi_i,V)$ is radical;
\item either $W(\pi_i,V)$ is empty or $(i-1)$-equidimensional;
\item $W(\pi_i,V)$ is smooth;
\item $\langle X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
\item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
\end{enumerate}
%
\begin{theorem}
Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
\end{theorem}
%
\begin{corollary} 
Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
\end{corollary}
%
%
%
%
\section{Weak Transversality}

@@

There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

@@

@@

@@

There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $D^{\textrm{?}}$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
\subsection{Sketch of the proof of Theorem 6.1}
Let 
Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
where $b_i$ is the i-th row of $A^{-1}$. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
Y_1(\xb),\hdots,Y_{i-1}(\xb), f(\xb),  \frac{\pa f(A\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(A\xb)}{\pa X_n}
has full rank, at all points $\xb \in \C^n$ with 
X_1(\xb)=\hdots,X_{i-1}(\xb)=f(\xb)= \frac{\pa f(xb)}{\pa X_{i+1}}=\hdots = \frac{\pa f(\xb)}{\pa X_{n}}=0.
Then we could use Theorem 5.1 to obtain a hypersurface with the desired properties. Let $\Phi$ be the mapping 
    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n+1} \\
       (Y_1,\hdots,Y_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
       \hdots&~,\grad(f(\xb))\cdot A_{n})),
We cannot directly define the appropriate polynomial mapping, as $Y_j(A\xb)$ is rational in $A^{-1}.$ To circumvent this issue, we can alternativly define a polynomial mapping $\Psi$ as  
    \Psi: \C^n \times \C^{n^2} \times \C &\rightarrow \C^{n+2} \\
           (\xb,A,T) &\mapsto 
       (\Yt_1,\hdots,\Yt_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
\hdots,\grad(f(\xb))\cdot A_{n}),&~T\cdot \det (A) - 1),
where $\Yt_j=TY_j$ with denominators cleared. Now, look at the points in $\Psi^{-1}(0).$ Here, $\det A \not = 0$ and therefore invertible, and therefore at all points in $\Psi^{-1}(0)$ the Jacobian matrix has full rank? 
For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank (i.e. $\Psi$ is transverse to $\{0\}).$
Thus, by Theorem 5.1, there exists a hypersurface $\Delta_2 \subset \C^{n^2}$, of degree at most $D^{n+1}$ with the property that if $A \in \C^{n^2}-\Delta_2$ then $\jac_{\xb}\Psi_A$ has full rank. $\hdots$ It then follows that for all $A \in \C^{n^2}-\Delta_2, \jac_{\xb}\Phi_A$ also has full rank. Therefore, by the Jacobian criterion, $f^A$ satisfies  $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$. 

@@

\section{Proof of Theorem 3.1}
Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$} 
Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$. Clearly then, if 
A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
\Delta = \prod_{i=1}^3 \D_i,
and note that 
\deg \D \leq  \prod_{i=1}^3 \deg \D_i.
Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
\section{Bit complexity}
Recall Theorem 1.1: \textit{Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the algorithm either produces a subset of the points or FAIL. In any case, the algorithm uses 
O^{\sim}(nk(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
O^{\sim}((s+D)D^n + nD^n).
}
Recall as well that the algorithm can error on one side by producing a proper subset of the points. Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
\subsection{The Algorithm}
For a matrix $A \in \GL(n,\Q),$ let 
Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
where $b_i$ is the i-th row of $A^{-1}$.
\begin{algorithm}[hbt!]
\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}D^{\td}$, where $\epsilon < 5/21$\;
\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
    \caption{{Main Algorithm} \label{}}
\nl \For{$i\gets1$ \KwTo $n$}{
\nl Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?)\; 
\nl Run \cite[Algorithm 2]{SH} $k > -\lg(1-2^{(-1/n)})$ times with input 
$\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } D$\;
\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
} 
\nl \Return $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$.
\end{algorithm}

%
\subsection{Proof of Theorem 1.1}
%
\textbf{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
%
\begin{enumerate}
    \item By our assumption on the size of $S$ we know that $|S| = \log (\epsilon^{-1}D^{\td}) \leq \td.$ Thus for $a_{ij} \in S$ we know that $|a_{ij}| \leq \td.$
    \item 
    \begin{enumerate}[label=\roman*.]
        \item $O(L)$ operations are required to compute $f$ from its straight line program $\Gamma.$
        \item After applying the change of variables obtaining $f(A x)=f^A(x)$ the height grows at most by a factor of
        \begin{align*}
        \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
        O(n\log n + n\log(D+1)) \\
        &= 
        O^\sim(\log(D+1)).
        \end{align*}
    \end{enumerate}
    \item After computing the partial derivatives the height grows by at most another factor of $\log D$. Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers. The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
    \item 
    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the
    following upper bound on the total number of bit operations required by the algorithm:
    \[
    O^\sim(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4))),
    \]
    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $D^n,$ and height at most
    \[
    O^{\sim}((s+D)D^n + nD^n).
    \]
\end{enumerate}
%
\par \noindent 
\textbf{Probability of success:} Note that when $\epsilon < 5/21$ (as stated in step 1 of Algorithm 1), then
\[
\pr[A \not \in \D] = 1-\epsilon > \frac{16}{21},
\]
so that after a single run of \cite[Algorithm 2]{SH}, the probability of success (ensuring all genericity properties and obtaining all points) is at least 
\[
\left( \frac{16}{21} \right) \left( \frac{21}{32} \right) = \frac{1}{2}.
\]
Thus, running \cite[Algorithm 2]{SH} $k$ times gives a list of outputs among which the highest cardinality set includes all points with probability at least $1-(1/2)^k$. We repeat this $n$ times to obtain $n$ zero-dimensional parameterizations. Thus, the probability that we have every point in each parameterization is $(1-(1/2)^k)^n$. We want 
\[
(1-(1/2)^k)^n>\frac{1}{2},
\]
which holds if and only if 
\[
k > -\lg(1-2^{(-1/n)}),
\]
thus proving Theorem 1.1. We can boost our success probability by running the main algorithm $\kt$ times, so that we obtain parameterizations whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1 - (1/2)^{\kt}$. 
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}
%%
\end{document}
\endinput
%%
%% End of file `sample-xelatex.tex'.

>>>>

%% %
%% \subsubsection{Critical points of polynomial mappings}
%% %
%% Let $\phi : V \rightarrow \C^m$ be a polynomial mapping. A \textit{critical point} of $\phi$ is a regular point of $V$ with $d_x \phi(T_xV) \not = \C^m,$ where $d_x \phi$ is the differential of $\phi$ at $x.$ A \textit{critical} value of $\phi$ is the image of a critical point by $\phi$.
%% %
%% \subsection{The zariski-tangent space}
%% %
%% Denote by $\grad_{\xb}(f)$ the evaluation of the gradient vector of $f$ in $\C[X_1,\hdots,X_n]$ at $\xb$ in $\C$.
%% The \textit{Zariski-tangent space} to $V$ at $\xb \in V$ is the vector space $T_{\xb}V$ defined by the equations $\grad_{\xb}(f) \cdot \textit{\textbf{v}}=0$ for all polynomials $f$ that vanish on $V$. For a polynomial system $\textit{\textbf{f}}=(f_1,\hdots,f_N)$ in $\C[X_1,\hdots,X_n]$, denote by $\jac(\textit{\textbf{f}})$ the Jacobian matrix.
%% The following is a direct consequence of \cite[Corollary 16.20]{ECA}.
%% %
%% \begin{proposition}
%% If $V \subset \C^n$ is a $d$-equidimensional algebraic set with ideal $I(V)=\langle f_1,\hdots,f_N \rangle$, then at any point $\textbf{x}$ of $\reg(V),$ $\jac_\textbf{x}(\textbf{f})$ has full rank $n - \dim(V)$ and the kernel of $\jac_\textbf{x}(\textbf{f})$ is equal to $T_\textbf{x}V.$ 
%% \end{proposition}
%% %
%% \subsection{Polar varieties}
%% %
%% %
%% \subsection{Changes of variables}
%
Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \xb \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
$V^A$ the set $\{x^A~|~\xb \in V\}, f^A$ the polynomial $f(A \xb)$ and $\xb^A$ denotes $A^{-1}\xb$. Notice $f^A(\xb^A) = f(A A^{-1}\xb)=f(\xb).$
%
%
%
%
%
%
%
%
\section{Genericity properties}
%
Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $d$.  
We say that $f$ satisfies $\textbf{H}$ if 
%
\begin{enumerate}
    \item $f$ is squarefree;
    \item $V(f) \cap \R^n$ is smooth.
\end{enumerate}
%
An equidimensional algebraic set $X$ of dimension $r$ is in \textit{Noether position} for $\pi_r$ when the extension 
\[
\C[X_1,\hdots,X_r] \rightarrow \C[X_1,\hdots,X_n]/I(V)
\] 
is injective and integral.  Then, for any $\xb \in \C^r,$ the fiber 
$V \cap \pi_r^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (\alpha_1,\hdots,\alpha_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
%
\begin{enumerate}
\item $\I(\pi_i,V)$ is radical;
\item either $W(\pi_i,V)$ is empty or $(i-1)$-equidimensional;
\item $W(\pi_i,V)$ is smooth;
\item $\langle X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
\item $V(X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
\item $V(X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
\item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
\end{enumerate}
%
\begin{theorem}
Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
\end{theorem}
%
\begin{corollary} 
Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
\end{corollary}
%
%
%
%
\section{Weak Transversality}

@@

There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

\subsection{Sketch of the proof of Theorem 4.1}

@@

\subsection{Proof of Theorem 4.1}

@@

Since $\deg \Phi_i \leq d,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then 
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
Let $p_{n-1} = (x_1,\hdots,x_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
X_1(\xb)-x_1,\hdots,X_{i-1}(\xb)-x_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
has full rank, at all points $(\xb,A) \in \C^n \times \C^{n^2}$ in the zero set of this system. It would then follow from Theorem 5.1 that a hypersurface  exists with the desired properties. 
Let $\Phi_i$ be the mapping 
    \Phi_i: \C^n \times \C^{i-1} &\rightarrow \C^{n} \\
           (\xb,\alpha_1,\hdots,\alpha_{i-1}) &\mapsto 
       (X_1(\xb)-\alpha_1,\hdots \\
       \hdots &,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n} ).
$\bz$ is a regular value of $\Phi_i.$
For all $(\xb,A) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ at $(\xb,A)$ has full rank $\td$. Indeed, the Jacobian is equal to

@@

@@

is integral.
%
%
%
%
\section{Proof of Theorem 3.1}
%
Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}. Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$} 
%
\begin{proof}
Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$. Clearly then, if 
\[
A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
\]
then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
\[
\Delta = \bigcup_{i=1}^3 \D_i,
\]
and note that 
\[
\deg \D \leq  \sum_{i=1}^3 \deg \D_i.
\]
\end{proof}
%
Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
%
\begin{proof}
\[
Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
\]
\end{proof}
%
%
%
%
\section{Bit complexity}
%
Recall Theorem 1.1: Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
  $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
  smooth.  Assume also that $f$ is given by a straight-line program
  $\Gamma$ of size $L$ with integer constants of height at most $b.$

  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
  as input and produces a zero-dimensional parameterization of a set
  that contains at least one point in each connected component of
  $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the
  algorithm either produces a subset of the points or FAIL. In any
  case, the algorithm uses
  \[
  O^{\sim}(k(Lb+d^{2n}(s+d)(L+d)))
  \]
  bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in
  the output have degree at most $d^n,$ and height $
  O^{\sim}((s+d)d^n).$

Recall as well that the algorithm can error on one side by producing a proper subset of the points. Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
%
\subsection{The Algorithm}
%
For a matrix $A \in \GL(n,\Q),$ let 
\[
Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
\]
where $b_i$ is the i-th row of $A^{-1}$.
%
\begin{algorithm}[hbt!]
\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}d^{\td}$, where $\epsilon < 5/21$\;
\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
    \caption{{Main Algorithm} \label{}}
\nl Randomly choose a point $p_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}~(p_0$?)\; 
\nl \For{$i\gets1$ \KwTo $n$}{
\nl Run \cite[Algorithm 2]{SH} $k > -\lg(1-2^{(-1/n)})$ times with input 
$\{Y_1-\alpha_1,\hdots,Y_{i-1}-\alpha_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
} 
\nl \Return $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$.
\end{algorithm}

%
\subsection{Proof of Theorem 1.1}
%
\textbf{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
%
\begin{enumerate}
    \item By our assumption on the size of $S$ we know that $|S| = \log (\epsilon^{-1}D^{\td}) \leq \td.$ Thus for $a_{ij} \in S$ we know that $|a_{ij}| \leq \td.$
    \item 
    \begin{enumerate}[label=\roman*.]
        \item $O(L)$ operations are required to compute $f$ from its straight line program $\Gamma.$
        \item After applying the change of variables obtaining $f(A x)=f^A(x)$ the height grows at most by a factor of
        \begin{align*}
        \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
        O(n\log n + n\log(d+1)) \\
        &= 
        O^\sim(\log(d+1)).
        \end{align*}
    \end{enumerate}
    \item After computing the partial derivatives the height grows by at most another factor of $\log d$. Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers. The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
    \item $\td$
    \item 
    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the
    following upper bound on the total number of bit operations required by the algorithm:
    \[
    O^\sim(kn(Lb+d^{2n}(s+d)(L+d))),
    \]
    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $d^n,$ and height at most
    \[
    O^{\sim}((s+d)d^n).
    \]
\end{enumerate}
%
\par \noindent 
\textbf{Probability of success:} Note that when $\epsilon < 5/21$ (as stated in step 1 of Algorithm 1), then
\[
\pr[A \not \in \D] = 1-\epsilon > \frac{16}{21},
\]
so that after a single run of \cite[Algorithm 2]{SH}, the probability of success (ensuring all genericity properties and obtaining all points) is at least 
\[
\left( \frac{16}{21} \right) \left( \frac{21}{32} \right) = \frac{1}{2}.
\]
Thus, running \cite[Algorithm 2]{SH} $k$ times gives a list of outputs among which the highest cardinality set includes all points with probability at least $1-(1/2)^k$. We repeat this $n$ times to obtain $n$ zero-dimensional parameterizations. Thus, the probability that we have every point in each parameterization is $(1-(1/2)^k)^n$. We want 
\[
(1-(1/2)^k)^n>\frac{1}{2},
\]
which holds if and only if 
\[
k > -\lg(1-2^{(-1/n)}),
\]
thus proving Theorem 1.1. We can boost our success probability by running the main algorithm $\kt$ times, so that we obtain parameterizations whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1 - (1/2)^{\kt}$. 
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}
%%
\end{document}
\endinput
%%
%% End of file `sample-xelatex.tex'.
